### 2022-04-26 README.Rmd
links to scenarios articles

---
output: github_document
bibliography: refs.bib
---

@@

See vignette [baseline scenario]() to see how this was modeled.

@@

See vignette [ENMAC scenario]() to see how this was modeled.

@@

See vignette [Intermodal scenario]() to see how this was modeled.

@@

See vignette [E-bike scenario]() to see how this was modeled.

@@

@@

We made use and developed a methodology that considers replacing long trips by bike + train or ferry trips (`name of the package`)

<!-- todo: include Robin's reflection about multi-modal trips replacement -->

>>>>

---
output: github_document
bibliography: refs.bib

---

@@

See vignette [baseline scenario](articles/0_baseline_scenario.html) to see how this was modeled.

@@

See vignette [ENMAC scenario](articles/1_enmac_scenario.html) to see how this was modeled.

@@

See vignette [Intermodal scenario](articles/2_intermodal_scenario.html) to see how this was modeled.

@@

See vignette [E-bike scenario](articles/3_ebikes_scenario.html) to see how this was modeled.

@@

<!-- figs not showing on pkgdown -->

@@

We made use and developed a [methodology](https://github.com/npct/rail) that considers replacing long trips by bike + train or ferry trips.
